\section{Purpose}
This document aims to describe, specify and analyze the software requirements for \textit{My Taxi Service}. \\
My Taxi Service is needed to provide a passenger-friendly interface to interact with the city's taxi service, and ensure
a fair management of the city-wide taxi deployment.


\section{Scope}
The passengers should be able to use an application (either mobile or browser based) to request a taxi through the system,
which in turn should answer with the ETA and identification code of the incoming tax. \\
The passengers should be compelled to provide their current location to the system, for their request to be accepted. \\
The taxi drivers should be able to use a mobile application to communicate their availability to the system, and accept
 or refuse incoming calls. \\
The system shall manage a queue of taxis for each taxi zone\footnote{See Definitions}. \\
The system shall receive GPS location data from each taxi, and use that information to assign each taxi to a 
taxi zone; an available taxi is automatically placed into the taxi queue belonging to the taxi zone it currently occupies. \\
The system shall remove a taxi from the queue upon receiving a confirmation in which the driver accepts an incoming call.
 If a taxi (driver) does, on the other hand, refuse an incoming call, the system
shall move it to the bottom of its taxi queue. \\
The system matches a passenger's position to a taxi zone, and uses that information to forward the call to the first taxi
available in the relative taxi queue. \\
The system shall provide an Application Programming Interface, to make room for future improvements. \\
The system shall also provide the possibility of requesting the reservation of a taxi; said reservation must occur at least
2 hours before the actual time of the ride; the time of the ride has to be specified by the passenger during the
reservation procedure, as well as the passenger's location and destination. \\
However, the system will actually allocate a taxi (by means of removing it from the queue) only 10 minutes before the
requested time of the ride. \\
On top of that, a ``taxi sharing'' option shall also be provided. The request of a shared ride shall trigger a process
in which the systems looks for other compatible taxi-sharing requests, computes an adequate route, and calculates
the amount of money each different passenger has to pay.

\section{Domain properties}
In this section we will analyze the background laying behind My Taxi Service:
\begin{itemize}
  % scrapped, because we can't assume that:
  %\item Passengers are assumed to be reliable and trustworthy, meaning that if they request a taxi or make a reservation
  %they will declare their real position and actually use the taxi
  \item Passengers will pay at the end of the ride the amount of money demanded by the taxi driver
  \item Passenger reserve a taxi only in a period of three month starting from the current time
  \item Taxi drivers must own a valid taxi driving license
  \item A taxi can reach every position within the same zone in less than 10 minutes
  \item ETA is estimated with a maximum error margin of 5 minutes and it's supplied by the map service our system will interact with
  \item We assume GPS coordinates reliable
  \item We assume that, for each zone, if its queue is empty, the system must notify the unavailability of taxis
 
\end{itemize}
\section{Goals}
The passengers must be able to:
\begin{itemize}
  \item [G1] Transmit its position and the desired destination to the system, thus initiating the Request of a taxi
  \item [G2] Receive the code and the ETA of the incoming taxi
  \item [G3] Reserve a taxi for a time period, starting at the time specified during the reservation\footnote{the starting of the
  reserved ride must occur at least 2 hours after the time of the reservation}, and ending after the ride is complete.
  \item [G4] Request a shared ride
\end{itemize}
The taxi driver must be able to:
\begin{itemize}
  \item [G5] Answer a passenger's request
  \item [G6] Render him/herself available to the scheduler
  \item [G7] Receive informations regarding the fee defined for each passenger
\end{itemize}
The system must be able to:
\begin{itemize}
  \item [G8] Offer a programmatic interface to enable the development of additional services
\end{itemize}


\section{Definitions, Acronyms and Abbreviations}
\begin{description}
  \item[Passenger:] the user who sends a taxi request.
  \item[User:] an human interacting with the system. Users are split in 2 classes: `passengers' and `taxi drivers'.
  \item[System:] the automatic part that manages the service.
  \item[ETA:] estimated time of arrival.
  \item[Taxi zones:] geographical partitions of the city, non overlapping, with an average size of 2Km\textsuperscript{2}.
  \item[Queue:] a list of all available taxis in the corresponding taxi zone. It is managed as a FIFO queue.
    There is exactly one taxi queue associated to each taxi zone.
  \item[GPS:] global position system.
  \item[Shared ride:] a passenger shares the ride with other people that origins from the same zone, and go to the same direction
  \item[Active reservation]: a reservation is considered active if it is in the reservation scheduler and isn't occured yet.
  \item[Same direction]: two taxi rdies are considered to be going in ``the same direction'' if and only if the destination taxi zone is the same.
\item [UI]: User interface
\end{description}


\section{Reference documents}


\section{Overview}

This document is structured in 6 parts:

\begin{itemize}
 \item [Introduction] in which it is explained the purpose of the software, and specific project-related terms are explained
 \item [Overall description] in which more focus is given to constraints and assumptions regarding the project
 \item [UI mockup] in which are given sample screenshots, preparatory for the prototyping of an actual application 
 \item [Specific requirements] in which requirements, both functional and non-functional, are fully explained.
 Use cases are also located there.
 
\end{itemize}
