\section{Overview}
% gps required
%TODO devo essere più preciso nella spiegazione delle funzioni dei vari componenti?
%TODO aggiungere anche il numero di tier e qualcosa di più specifico sulla parte hardware?
The distributed application is composed by a server side, and a client one.
The client side interacts with users ( or guests), showing the correct activity, and send requests to the server sdie, when needed.
The client side must be able to interact with the GPS,
The server side manages requests comeing from the client side, and notify the users ( or the guests) involved in the requests.
The server side must also interact with a map system, in order to retreives information about the route and the km of the ride.
\section{High level components and their interaction}
% aggiungere l'UML che ho fatto per il RASD?
The client side is composed by a set of activity composed by one or more actions and displayed through the user interface.
The client side has also an interface that manage that manage the interaction with the server.
The server side has a controller for each connected client, that manages the requests comeing from the users ( or guests), 
taking data from the ride manager. It also sends messages to the clients in order to resolve the requests.
The controller interacts with the clients through a network interface.
\section{Component view}
	\subsection{Client}
	 \begin{itemize}
	  \item [Activity]: an activity is a set of messages and actions, that the application must display to the users.
	  No more than one activity can be displayed at the same time;
	  The default activity is the "guest home" activity. Each time the user taps a button, the application must execute
	  the related action, and select the next activity. 
	  \item [Action]: an action is something that a user can do, in order to interact with the application.
	  If an action need some data, the userinterface must display a field ,for each input needed, that allows the human
	  to provide the necessary incormations.
	  Some actions can also select the next activity that must be shown, or/and send informations to the server,
	  in order to complete their job.
	  \item [Userinterface]: is the component that directly interact with the human.
	  It contains the activity that must be displayed, and read the components of the activity, in order to display them.
	  It also launch the actions selected by the human.
	  \item[Clientnetworkinterface]: is the component that allow the others to exchange messages with the server sdie.
	 \end{itemize}
	\subsection{Server}
	\begin{itemize}
	 \item [Controller]: we have one conroller for each client connected; initially will be a guest controller,
	 that allow to login/register. After a succesfull login, the guest controller will create a taxi driver/passenger controller,
	 and substitutes himself with the new controller. The controller must manage requests comeing from
	 the client, taking informations from the ridesmanager, and eventually adding new objects to him.
	 In order to sends and receives message from the client, the controller communicates with a Servernetworkinterface.
	 The controller also contains a User object, that allows him to retrieves information about the specific logged user.
	 \item [Ridesmanager]: it is a singleton, that contains informations about the queues, the active rides. This corresponds 
	 to the model in the MVC pattern and it is shared by all the controllers.
	 \item [User]: is the component that contains every possible information about a logged user, taken from the database.
	 User is a part of the controller ( obviously only in case of passenger/taxi driver controller).
	 User is splitted in taxi driver and passenger, cause there are some differences between the two kind of user.
	 Also user is a part of the model, but it is not shared.
	 \item[Servernetworkinterface]:
	\end{itemize}
\section{Runtime view}
% sequence diagrams
% sequence for: login
% sequence for: registration
% sequence for: taxi request
% sequence for: refused call
% sequence for: update taxi position
% sequence for: shared taxi ride

\section{Component interfaces}
% socket?

\section{Selected architectural styles and patterns}
% client - server
% MVC

\section{Other design decisions}
% hw architecture (see diagram)
% distributed application servers (not in the same physical local network) -> abstraction -> just like big G
% we exclude a priori the possibility of a water-powered machine