%TODO: team talk about this part
\begin{itemize}
 \item[G1]: clicking on the button contained in the passenger home activity, a taxi request form will be shown. 
  Filling the form allows the user to make a taxi request.
 \item[G2]: as soon as a taxist decides to take care about a call, the controller asks the map service to calculate an ETA. 
 After that, the system will notify the passenger's client, that will display those information through an ad hoc activity.
 \item[G3]: when a taxi driver accepts to take care about a call, his controller will remove him from the queue.
 \item[G4]: in order to request a shared ride, a passenger must fill the form for a reservation/request, and add the shared option;
 The server will create a ride object, search for a sharedride that respect the constraints explained in the RASD document,
 and add the ride object to the shared ride; otherwise a new sharedride will be created.
 \item[G5]: when the taxi driver's client receive a call notification from the server, the application will select and display 
 and ad hoc activity, that allow the taxi driver to click on "accept" or "refuse". After that, the client will send a message to the
 server, in order to inform him about the human's decision.
 \item[G6]: the taxi driver home activity provide a button that switch the taxist status; it will requests the controller to 
 remove/ add himself to a taxi queue.
 \item[G7]: when a taxists accepts to take care about a requests ( either shared or not), the controller will notify the client about
 the ETA and the fee amount. The client will display an ad hoc activity for these informations.
 \item[G8]: %TODO 
\end{itemize}